---
title: "AssociationRuleAnalysis"
author: "Zhichao Yuan(zxy180004)"
date: "April 16, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required Library

We need following libraries

```{r message=FALSE, warning=FALSE}
require(readr)
require(arules)
require(dplyr)
```

# Preprocessing data

First, We read data from file from original data file which is downloaded from kaggle. For the data file "order_products__train.csv", if we read the whole data, we cannot process it in the PC momery later, so we just use the first 20000 rows in the data.

Then, we process and extract useful informations into transaction_product_data and transaction_department_data.

Finally, we convert them to classes of transactions, product_as_transaction and department_as_transaction.

```{r warning=FALSE}
# preprocessing data

# read data from file
order_products_data<-read.csv("https://github.com/lypf2018/InstacartMarketBasketAnalysisKaggle/raw/master/dataset/order_products__train.csv", nrows=20000)
products_data<-read.csv("https://github.com/lypf2018/InstacartMarketBasketAnalysisKaggle/raw/master/dataset/products.csv")
department_data<-read.csv("https://github.com/lypf2018/InstacartMarketBasketAnalysisKaggle/raw/master/dataset/departments.csv")

# getting order and product id from order_products_data
order_product_id_data<-order_products_data[,1:2]
# get product id, name and department id from products_data
product_department_data<-products_data[,c(1:2,4)]

# merging to transection information data and sorting
product_department_with_name_data<-merge(product_department_data, department_data, by="department_id")
transaction_data<-merge(order_product_id_data, product_department_with_name_data, by="product_id")
transaction_data<-arrange(transaction_data, order_id)

# extracting product analysis data needed
product_analysis_data<-transaction_data[,c(2,4)]
department_analysis_data<-transaction_data[,c(2,5)]

# Splitting the data
transaction_product_data <- split(product_analysis_data$product_name, product_analysis_data$order_id)
transaction_department_data <- split(department_analysis_data$department, department_analysis_data$order_id)

# Converting data to a class of transactions
product_as_transaction = as(transaction_product_data,"transactions")
department_as_transaction = as(transaction_department_data,"transactions")

```

# Finding frequent itemsets and Association rules

## 1. Frequent itemsets for products in orders dataset.
```{r}
# 1. Frequent itemsets for products in orders dataset.
frequentItems <- eclat(product_as_transaction, parameter = list(supp = 0.07, maxlen = 15))
inspect(frequentItems)
# plot frequent itemsets for products
itemFrequencyPlot(product_as_transaction, topN=10, type="absolute", main="Item Frequency")
```

## 2. Association rules for products in orders dataset.
```{r}
# 2. Association rules for products in orders dataset.
rules <- apriori(product_as_transaction, parameter = list(supp = 0.001, conf = 0.5, maxlen=15))
# 'high-confidence' rules.
rules_conf <- sort(rules, by="confidence", decreasing=TRUE)
# show the support, lift and confidence for all rules
inspect(head(rules_conf))
```

## 3. Frequent itemsets for departments in orders dataset.
```{r}
# 3. Frequent itemsets for departments in orders dataset.
frequentItems <- eclat(department_as_transaction, parameter = list(supp = 0.07, maxlen = 15))
inspect(frequentItems)
# plot frequent itemsets for products
itemFrequencyPlot(department_as_transaction, topN=10, type="absolute", main="Item Frequency")
```

## 4. Association rules for departments in orders dataset.
```{r}
# 4. Association rules for departments in orders dataset.
rules <- apriori(department_as_transaction, parameter = list(supp = 0.001, conf = 0.5, maxlen=15))
# 'high-confidence' rules.
rules_conf <- sort(rules, by="confidence", decreasing=TRUE)
# show the support, lift and confidence for all rules
inspect(head(rules_conf))
```
